The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex

This implies that when searching for the maximal exponent defining {\tt nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of {\tt nu(e-1,I,J)}, and one needn't search too far past this number.  This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each $s = 0,\ldots,e$.  This is indeed how the computation is done in most cases.

@@

%\newpage
\section{Future Directions}
\label{sec.FutureDirections}

@@

\begin{enumerate}
\item Add more cases to {\tt UseSpecialAlgorithms}.
\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.

@@

\bibliographystyle{skalpha}
\bibliography{MainBib}

>>>>

This implies that when searching for the maximal exponent defining {\tt nu(e,I,J)} for positive $e$, it is safe to start at $p$ times the output of {\tt nu(e-1,I,J)}, and one needn't search too far past this number.  This also suggests that the most efficient way to compute {\tt nu(e,I,J)} is to compute, successively, {\tt nu(s,I,J)}, for each integer $s = 0,\ldots,e$.  This is indeed how the computation is done in most cases.

@@

\newpage
\section{Future Directions}
\label{sec.FutureDirections}

@@

\begin{enumerate}
\item Add more cases to {\tt UseSpecialAlgorithms}.
%\item Add the capability to compute non-local {\tt fpt} and non-local {\tt nu} via an option.
\item Write a function that will extract from this sequences $\{ \nu_f^{\idealm}(p^e) \}_{e=1}^{\infty}$ roots of Bernstein-Sato polynomials.  Especially, strata.

@@

\newpage
\bibliographystyle{skalpha}
\bibliography{MainBib}
